### 2023-04-04 chapter2/chapter2.tex
Added new methods section for definition of features
Added citation for scikit-learn

@@

\subsection{Code and data availability}
The code used to produce the results and analyses is available at \url{https://github.com/marcsingleton/IDR_evolution2023}. The following Python libraries were used: matplotlib, NumPy, pandas, and SciPy~\cite{Hunter2007, Harris2020, McKinney2010, Virtanen2020}. Relevant output files are available in the supporting information. There is no primary data associated with this manuscript. All primary data are available from publicly accessible sources described in their corresponding sections.

>>>>

\subsection{Definition and calculation of features}

@@

\subsection{Code and data availability}
The code used to produce the results and analyses is available at \url{https://github.com/marcsingleton/IDR_evolution2023}. The following Python libraries were used: matplotlib, NumPy, pandas, SciPy, and scikit-learn~\cite{Hunter2007, Harris2020, McKinney2010, Virtanen2020, Pedregosa2011}. Relevant output files are available in the supporting information. There is no primary data associated with this manuscript. All primary data are available from publicly accessible sources described in their corresponding sections.
